\documentclass[hyperref={pdfpagelabels=false}]{beamer}
%%% workaround: http://tex.stackexchange.com/questions/4436/beamer-undefined-control-sequence
\providecommand\thispdfpagelabel[1]{}
%%%
\usepackage{beamerthemesplit}
\usepackage{lmodern}
\title{Using the Shell}
\author{UIC Linux Users Group}
\date{\today}
\begin{document}
\frame{\titlepage}
\section{Getting Started}
\subsection{Open a Shell}
\frame
{
    This is an interactive presentation.
    \begin{itemize}
    \item{Login}
        \begin{itemize}
        \item{Ask if you need help.}
        \end{itemize}
    \item{ Click on Applications$\Rightarrow$Utilities$\Rightarrow$Terminal}
    \item{ Type 'bash' (Enter) for a real shell.}
    \end{itemize}
   
}
\subsection{A Shell, what is it?}
\frame
{
    \frametitle{A Shell, what is it?}
    \begin{itemize}
    \item{It interprets commands from the user.}
    \item{Passes control to other programs.}
    \item{Supports batch operations via scripting.}
    \item{bash is one of many shells.}
        \begin{itemize}
        \item{sh, csh, tcsh, zsh, etc.}
        \end{itemize}
    \end{itemize}
}
\section{Directory Navigation}
\subsection{List (ls)}
\frame
{
    \frametitle{List (ls)}
    Lists files and directories.
    \begin{itemize}
    \item{Directories are equivalent to folders.}
    \end{itemize}
    \begin{itemize}
    \item{ls}
    \item{ls -l}
    \item{ls -a}
    \item{ls -la}
    \end{itemize}
}
\frame
{
    \frametitle{List (ls) (continued)}
    \begin{itemize}
    \item{Wildcards (* and ?)}
    \item{more}
        \begin{itemize}    
        \item{ls -l $\mid$ more}
        \end{itemize}
    \end{itemize}
}
\subsection{bash Tips}	
\frame
{
    \frametitle{Random bash Tips}
    \begin{itemize}
    \item{Tab Completion}
    \item{Command History}
    \end{itemize}
}
\subsection{Directory Commands}
\frame
{
    \frametitle{Directory Commands}
    \begin{itemize}
    \item{pwd}
    \item{mkdir {\textless}directory\textgreater\hspace{.5 pc}}
    \item{rmdir {\textless}directory\textgreater\hspace{.5 pc}}
    \end{itemize}
}
\subsection{Change Directory (cd)}
\frame
{
    \frametitle{Change Directory (cd)}
    Changes the current working directory.
    \begin{itemize}
    \item{cd {\textless}directory\textgreater}
    \item{cd /}
        \begin{itemize}
        \item{All locations start here.}
        \item{No drives like on Windows or DOS.}
        \end{itemize}
    \item{cd $\sim$ (or just cd)}
        \begin{itemize}
        \item{Taks you to /home/{\textless}your username\textgreater}
        \end{itemize}
    \end{itemize}
}
\frame
{
    \frametitle{Change Directory (cd) - Relative Navigation}
    \begin{itemize}
    \item{cd ./}
    \item{cd ../}
    \item{cd ../../someotherplace/}
    \end{itemize}
}
\subsection{Mount Points}
\frame
{
    \frametitle{Mount Points}
    All physical volumes are part of the same hierarchy.
    \begin{itemize}
    \item{Mount points are found under /mnt and /media.}
    \item{mount {\textless}device\textgreater\hspace{.5 pc}{\textless}mount point\textgreater\hspace{.5 pc}}
    \item{umount {\textless}mount point\textgreater\hspace{.5 pc}}
    \end{itemize}
}
\subsection{Moving, Copying and Deleting}
\frame
{
    \frametitle{Moving, Copying and Deleting}
    \begin{itemize}
    \item{touch} {\textless}file\textgreater\hspace{.5 pc}
        \begin{itemize}
        \item{Use it to create empty files.}
        \end{itemize}
    \item{mv -i {\textless}source\textgreater\hspace{.5 pc}{\textless}destination\textgreater\hspace{.5 pc}}
	\begin{itemize}
        \item{Rename and Move}
        \end{itemize}
    \item{cp -i {\textless}source\textgreater\hspace{.5 pc}{\textless}destination\textgreater\hspace{.5 pc}}
    \item{rm -i {\textless}file(s)\textgreater\hspace{.5 pc}}
	\begin{itemize}
        \item{rm -rfI {\textless}directory(ies)\textgreater\hspace{.5 pc}}
        \end{itemize}
    \end{itemize}
}
\section{Permissions}
\subsection{Example Shell Script}
\frame
{
    \frametitle{Example Shell Script}
    echo \textbackslash\#\textbackslash!/bin/sh \textgreater \hspace{.5 pc}temp.sh\\
    echo echo \textbackslash"Hello world\textbackslash!\textbackslash{\textbackslash}n\textbackslash" \textgreater\textgreater \hspace{.5 pc}temp.sh
}
\frame
{
    \frametitle{Example Shell Script (continued)}
    \begin{itemize}
    \item{cat temp.sh}
    \item{echo}
    \item{\#!}
    \item{File Redirection}
    \end{itemize}
}
\subsection{File Permissions}
\frame
{
    \frametitle{File Permissions}
    \begin{itemize}
    \item{chmod {\textless}permission\textgreater\hspace{.5 pc}file(s)}
        \begin{itemize}
        \item{Read u+r (r\hspace{.1 pc}-\hspace{.1 pc}-)}
        \item{Write u+w (-\hspace{.1 pc}w\hspace{.1 pc}-)}
        \item{Execute u+x (-\hspace{.1 pc}-\hspace{.1 pc}x)}
            \begin{itemize}
            \item{chmod u+x temp.sh}
            \item{./temp.sh}
            \end{itemize}
        \end{itemize}
    \item{ls -l}
    \end{itemize}
}
\subsection{Directory Permissions}
\frame
{
    \frametitle{Directory Permissions}
    \begin{itemize}
    \item{chmod {\textless}permission\textgreater\hspace{.5 pc}directory(ies)}
        \begin{itemize}
        \item{Read u+r (r\hspace{.1 pc}-\hspace{.1 pc}-)}
        \item{Write (-\hspace{.1 pc}w\hspace{.1 pc}-)}
        \item{Traverse (-\hspace{.1 pc}-\hspace{.1 pc}x)}
        \end{itemize}
    \item{ls -l}
        \begin{itemize}
        \item{d\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-}
        \end{itemize}
    \end{itemize}
}
\subsection{User, Group, Other Permissions}
\frame
{
    \frametitle{User, Group, Other Permissions}
    \begin{itemize}
    \item{chmod u+rwx {\textless}file(s)\textgreater\hspace{.5 pc}(-\hspace{.1 pc}r\hspace{.1 pc}w\hspace{.1 pc}x\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-)}
    \item{chmod g+rwx {\textless}file(s)\textgreater\hspace{.5 pc}(-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}r\hspace{.1 pc}w\hspace{.1 pc}x\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-)}
    \item{chmod o+rwx {\textless}file(s)\textgreater\hspace{.5 pc}(-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}-\hspace{.1 pc}r\hspace{.1 pc}w\hspace{.1 pc}x)}
    \end{itemize}
    \begin{itemize}
    \item{chmod u-rw {\textless}file(s)\textgreater\hspace{.5 pc}}
    \item{chmod a+rx {\textless}file(s)\textgreater\hspace{.5 pc}}
    \item{chmod 755 {\textless}file(s)\textgreater\hspace{.5 pc}(-\hspace{.1 pc}r\hspace{.1 pc}w\hspace{.1 pc}x\hspace{.1 pc}r\hspace{.1 pc}-\hspace{.1 pc}wr\hspace{.1 pc}-\hspace{.1 pc}w)}
    \end{itemize}
}
\subsection{Complex Permissions}
\frame
{
    \frametitle{User, Group, Other Permissions}
    \begin{itemize}
    \item{-\hspace{.1 pc}r\hspace{.1 pc}w\hspace{.1 pc}s\hspace{.1 pc}r\hspace{.1 pc}-\hspace{.1 pc}S\hspace{.1 pc}r\hspace{.1 pc}-\hspace{.1 pc}t}
    \item{Layered directories to support complex permissions.}
    \item{Access Control Lists}
        \begin{itemize}
        \item{Security Enhanced Linux}
        \end{itemize}
    \end{itemize}
}
\subsection{Symlinks}
\frame
{
    \frametitle{Symlinks}
    \begin{itemize}
    \item{Can be used for security.}
    \item{Hard and Soft Links}
    \item{ln -s {\textless}realfile\textgreater\hspace{.5 pc}{\textless}symlink\textgreater\hspace{.5 pc}}
        \begin{itemize}
        \item{Like a Windows Shortcut.}
        \item{More Transparent.}
        \end{itemize}
    \end{itemize}
}
\section{Other Important Commands and Applications}
\subsection{Environment Variables}
\frame
{
    \frametitle{Environment Variables}
    \begin{itemize}
    \item{echo \$TERM}
    \item{export TERM="xterm"}
    \item{\$SHELL \$DISPLAY \$HOSTNAME \$JAVA \$PATH}
    \end{itemize}
}
\subsection{Text Editors}
\frame
{
    \frametitle{Text Editors}
    \begin{itemize}
    \item{Newbies use pico or nano.}
    \item{Real Linux users use vim.}
        \begin{itemize}
        \item{Weird people use emacs.}
        \end{itemize}
    \end{itemize}
}
\subsection{Other Commands}
\frame
{
    \frametitle{Other Commands}
    \begin{itemize}
    \item{man}
    \item{Ctrl-C}
    \item{backtick (`)}
    \item{screen}
    \end{itemize}
}
\section{Questions}
\frame
{
    \frametitle{Questions?}
    Questions?
}
\section{About LUG/ACM}
\frame
{
    \frametitle{About the UIC-LUG \& UIC-ACM}
    UIC LUG
    \begin{itemize}
    \item{lug.cs.uic.edu/contaxt}
    \item{email SUBSCRIBE to lug@listserv.uic.edu}
    \item{in SEL 2260 (Next Door)}
    \end{itemize}
    UIC ACM
    \begin{itemize}
    \item{ACM Office: SEL East 2262}
    \item{Meetings on select Thursdays at 5:30 PM}
    \item{in SEO 1000}
    \end{itemize}
}
\end{document}
